Predicting computational reproducibility of scientific pipelines using collaborative filtering

### 2018-07-11 paper.tex
Some text in the intro

@@

>>>>

We consider the problem of predicting the values of a variable 
controlled by a hidden, parametrized, time dependent, deterministic 
process over time. We assume that the variable values is observed only for 
a limited number of time points, and we aim at predicting the values in the remaining time points.

We approach the problem from the point of view of collaborative 
filtering. The process is represented by a matrix where columns 
represent different parametrizations (we do not assume an order on the 
parametrizations) and rows represent the time points. The main difference with the traditional 
collaborative filtering problem

% This is just a working example

@@

% Other possible examples

Seasonality of MS lesions.
Thresholded stock values.
